\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Deepak Kumar Upadhayay} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+36 703029295 \\ Budapest, HU} 
\address{\href{dku3132@gmail.com}{dku3132@gmail.com} \\ \href{https://www.linkedin.com/in/deepak-dd79dy/}{linkedin.com/in/deepak-dd79dy/} \\ \href{https://github.com/inspironman}{github.com/inspironman}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Computer Science student, seeking for Internship}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Sc Computer Science}, Eötvös Loránd University (ELTE) \hfill {Expected 2024}\\
 
{\bf Higher Secondary Education}, D.A.V Public School \hfill {2018 - 2020}\\
Physics,Chemistry,Maths and Information Practices {12th} \hfill {\bf 91.4\%}\\
English,Science,Social Science and Information Practices {10th} \hfill {\bf 95.4\%}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Technical Skills & A, B, C, D
% \\
% Soft Skills & A, B, C, D\\
% XYZ & A, B, C, D\\
C/C++, Java, Python, Clean [ Functional Programming ]\\ 
HTML/CSS, JavaScript, PHP, SQL \\
Linux, Git/GitHub, IoT Fundamentals and Big Data
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Teaching Assistant of Algorithm and Data Structure I} \hfill Present\\
Eotvos Lorand University \hfill \textit{Budapest, HU}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Assisting Professor in planning and preparing the lecture.
     \item Conducting doubt sessions for students.
    \item Evaluating exams and assignments. 
 \end{itemize}
 
\textbf{Student Mentor} \hfill Present\\
HÖOK Stipendium Hunaricum Mentor Network \hfill \textit{Budapest, HU}
 \begin{itemize}
    \itemsep -1pt {} 
     \item Assisting new students in their educational and documentation procedure at the University. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Voting Poll} {A web application using PHP where logged-in users can cast their votes on polls.Admin users can create,delete or edit polls. \href{https://github.com/inspironman/Voting-Poll}{(Try it here)}}
\item \textbf{Light the Bulb} Light the Bulb is a Puzzle Game using Javascript, HTLM/CSS. \href{https://lightthebulb.netlify.app}{(Try it here)}}}
\item \textbf{Creature Life Cycle} {Simulation of Creature Life Cycle in C++ using visitor design pattern \href{https://github.com/inspironman/Creature-Life-Cycle-}{(Github Link)}}
\item \textbf{Gambling Game} {Slot machine Gambling Game using basics of Python and modules like random and os.\href{https://github.com/inspironman/Gambling-Game}{(Github)}}
\item \textbf{Chess Matrix} {Implement the chessboard matrix type which contains integers. In these matrices, every second entry is zero. The entries that can be nonzero are located like the samecolored squares on a chessboard.\href{https://github.com/inspironman/Chess_Matrix}{(Github)}}
\item \textbf{Minesweeper} {Minesweeper is logic-based computer game developed in C. Predetermined number of randomly-placed "mines" in the shortest possible time by clicking on "safe" squares while avoiding the squares with mines.\href{https://github.com/inspironman/MineSweeper}{(Github)}}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
    \item\href{https://stipendiumhungaricum.hu/}{Stipendium Hungaricum Scholarship} Fully Funded Scholarship by Hungarian Government and Tempus Public Foundation to pursue my B.Sc Computer Science at Eötvös Loránd University, Hungary.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item 
% \end{itemize}
% \end{rSection}


\end{document}
